P versus NP

### 2019-12-04 doc/manuscript.tex
The content proof was slighlty modified

In previous years there has been great interest in the verification or checking of computations \cite{LIP90}. Interactive proofs introduced by Goldwasser, Micali and Rackoff and Babi can be viewed as a model of the verification process \cite{LIP90}. Dwork and Stockmeyer and Condon have studied interactive proofs where the verifier is a space bounded computation instead of the original model where the verifer is a time bounded computation \cite{LIP90}. In addition, Blum and Kannan has studied another model where the goal is to check a computation based solely on the final answer \cite{LIP90}. More about probabilistic logarithmic space verifiers and the complexity class $NP$ has been investigated on a technique of Lipton \cite{LIP90}. In this work, we show some results about the logarithmic space verifiers applied to the class $NP$ and logarithmic space disqualifiers applied to the class $coNP$ which solve one of the most important open problems in computer science, that is $P$ versus $NP$.

@@

A logarithmic space transducer is a Turing machine with a read-only input tape, a write-only output tape, and read/write work tapes \cite{MS06}. The work tapes must contain at most $O(\log n)$ symbols \cite{MS06}. A logarithmic space transducer $M$ computes a function $f : \Sigma^{*} \rightarrow \Sigma^{*}$, where $f(w)$ is the string remaining on the output tape after $M$ halts when it is started with $w$ on its input tape \cite{MS06}. We call $f$ a logarithmic space computable function \cite{MS06}. We say that a language $L_{1} \subseteq \{0, 1\}^{*}$ is logarithmic space reducible to a language $L_{2} \subseteq \{0, 1\}^{*}$, written $L_{1} \leq_{l} L_{2}$, if there exists a logarithmic space computable function $f : \{0, 1\}^{*} \rightarrow \{0, 1\}^{*}$ such that for all $x \in \{0, 1\}^{*}$,
\[x \in L_{1} \textit{ if and only if } f(x) \in L_{2}.\]
The logarithmic space reduction is frequently used for $L$ and $NL$ \cite{Pap03}. A Boolean formula is in 2-conjunctive normal form, or $2CNF$, if it is in $CNF$ and each clause has exactly two distinct literals. There is a problem called $2SAT$, where we asked whether a given Boolean formula $\phi$ in $2CNF$ is satisfiable. $2SAT$ is complete for $NL$ \cite{Pap03}. Another special case is the class of problems where each clause contains $XOR$ (i.e. exclusive or) rather than (plain) $OR$ operators. This is in $P$, since an $\textit{XOR SAT}$ formula can also be viewed as a system of linear equations mod $2$, and can be solved in cubic time by Gaussian elimination \cite{MM11}. We denote the $XOR$ function as $\oplus$. The $\textit{XOR 2SAT}$ problem will be equivalent to $\textit{XOR SAT}$, but the clauses in the formula have exactly two distinct literals. $\textit{XOR 2SAT}$ is in $L$ \cite{AR00}, \cite{RM08}.

@@

\begin{hypothesis}
\label{hypothesis1}
Given a nonempty language $L_{1} \in L$, there is a language $L_{2}$ in $\textit{NP--complete}$ with a deterministic Turing machine $M$, where:
\[L_{2} = \{w: M(w, u) = y \textit{ for some string } u \textit{ such that } y \in L_{1}\}\]
when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$. In this way, there is an $\textit{NP--complete}$ language defined by a logarithmic space verifier $M$ such that when the input is an element of the language with its certificate, then $M$ outputs a string which belongs to a single language in $L$.
\end{hypothesis}

@@

$coNL$ is the complexity class containing the languages when their complements belong to $NL$ \cite{Pap03}. We can give a disqualification-based definition for $coNL$ \cite{AB09}. The disqualification-based definition of $coNL$ assumes that a logarithmic space Turing machine has another separated read-only tape, that is the same kind of special tape called $``$read-once$"$ that we use in the certificate-based definition for $NL$ \cite{AB09}. Besides, in the disqualification-based definition of $coNL$, we assume the disqualification string is appropriated for the instance \cite{Pap03}. For example, a truth assignment for a Boolean formula $\phi$ in $3CNF$ is appropriated for the instance when every possible variable in $\phi$ could be evaluated in that truth assignment string, but we cannot affirm the same for every possible binary string.

@@

\begin{hypothesis}
\label{hypothesis2}
Given a nonempty language $L_{1} \in 1NL$, there is a language $L_{2}$ in $\textit{coNP--complete}$ with a deterministic Turing machine $M$, where:
\[L_{2} = \{w: M(w, u) = y \textit{ for all the appropriated string } u \textit{ such that } y \in L_{1}\}\]
when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$. In this way, there is a $\textit{coNP--complete}$ language defined by a logarithmic space disqualifier $M$ such that when the input is an element of the language with any of its appropriated disqualification, then $M$ always outputs a string which belongs to a single language in $1NL$.
\end{hypothesis}

@@

\begin{theorem}
\label{proof}
There is a deterministic Turing machine $M$, where:
\[MAX\oplus2SAT = \{w: M(w, u) = y \textit{ for some string } u \textit{ such that } y \in \textit{XOR 2SAT}\}\]
when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
\end{theorem}

@@

\begin{proof}
Given a collection of integers $C$, we can read its elements from left to right, verify that every element is not equal to $0$, check that every element in $C$ has the same bit-length and count the amount of elements in $C$ to finally multiply it by $3$ and compare its bit-length with the single bit-length from the elements in $C$. In addition, we can nondeterministically pick two elements $a$ and $b$ from $C$ and accept in case of $a + b = 0$ otherwise we reject. We can make all this computation in a nondeterministically one-way using logarithmic space. Certainly, the calculation and store of the bit-length of the elements in $C$ could be done in logarithmic space since this is a unique value. On the one hand, we can count and store the number of elements that we read from the input and multiply it by $3$ to finally compare its bit-length with the stored bit-length, since the cardinality of $C$ multiplied by $3$ could be stored in a binary number of bit-length that is logarithmic in relation to the encoded length of $C$. On the other hand, the two elements $a$ and $b$ that we pick from $C$ have a logarithmic space in relation to the encoded length of $C$, because of every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$. Indeed, we never need to read to the left on the input for the acceptance of the elements in $\textit{SUM--ZERO}$ in a nondeterministically logarithmic space.
\end{proof}

\begin{theorem}
\label{demonstration}
There is a deterministic Turing machine $M$, where:
\[3UNSAT = \{w: M(w, u) = y \textit{ for all the appropriated string } u \textit{ such that } y \in \textit{SUM--ZERO}\}\]
when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
\end{theorem}

@@

\begin{algorithm}
\caption{Logarithmic space disqualifier}\label{algorithm2}
\begin{algorithmic}[1]
\Comment{A valid instance for $3UNSAT$ with its disqualification}
\Procedure{$\textit{DISQUALIFIER}$}{$\phi, A$}
\Comment{Initialize an index}
\State $j \gets 0$
\Comment{$m$ is the number of clauses in $\phi$}
\Comment{Iterate for the elements of the disqualification array $A$}
\For{$i$}{$1$}{$m + 1$}
\If{$i = m+1$}
\Comment{There exists an $m+1$ element in the array}
\If{$A[i] \neq \textit{undefined}$}
\Comment{Reject the disqualification}
\State \textbf{return} $``no"$
\EndIf
\Comment{Break the for loop}
\State \textbf{break}
\ElsIf{$A[i] = \textit{undefined} \vee A[i] < 1 \vee A[i] > 3$}
\Comment{Reject the disqualification}
\State \textbf{return} $``no"$
\Else
\State $j \gets A[i]$
\EndIf
\Comment{From the indexed $i^{th}$ clause $c_{i} = (x_{j} \vee y_{k} \vee z_{r})$ in $\phi$}
\Comment{Where $x$, $y$ and $z$ are literals with local indexes $\{j, k, r\} = \{1,2,3\}$ in $c_{i}$}
\Comment{Output the integer of the $j^{th}$ literal filled with zeroes until $|3 \times m|$ bits}
\State \textbf{output} $``x_{j}"$
\EndFor
\EndProcedure
\end{algorithmic}
\end{algorithm}
\end{proof}

@@

\begin{proof}
Since we have is true either $L \neq NL$ or $L = NL$, then the complexity class $P$ is equal to $NP$.
\end{proof}

@@

No one has been able to find a polynomial time algorithm for any of more than $300$ important known $\textit{NP--complete}$ problems \cite{GJ79}. A proof of $P = NP$ will have stunning practical consequences, because it leads to efficient methods for solving some of the important problems in $NP$ \cite{CS00}. The consequences, both positive and negative, arise since various $\textit{NP--complete}$ problems are fundamental in many fields \cite{CS00}. All the following consequences are assuming that we have a practical solution for the $\textit{NP--complete}$ problems where such existence was proven with our nonconstructive result:

Cryptography, for example, relies on certain problems being difficult. A constructive and efficient solution to an $\textit{NP--complete}$ problem such as $3SAT$ will break most existing cryptosystems including: Public-key cryptography \cite{HW97}, symmetric ciphers \cite{MM00} and one-way functions used in cryptographic hashing \cite{DKV07}. These would need to be modified or replaced by information-theoretically secure solutions not inherently based on $\textit{P--NP}$ equivalence.

There are enormous positive consequences that will follow from rendering tractable many currently mathematically intractable problems. For instance, many problems in operations research are $\textit{NP--complete}$, such as some types of integer programming and the traveling salesman problem \cite{GJ79}. Efficient solutions to these problems have enormous implications for logistics \cite{CS00}. Many other important problems, such as some problems in protein structure prediction, are also $\textit{NP--complete}$, so this will spur considerable advances in biology \cite{BL98}.

Since all the $\textit{NP--complete}$ optimization problems become easy, everything will be much more efficient \cite{LF09}. Transportation of all forms will be scheduled optimally to move people and goods around quicker and cheaper \cite{LF09}. Manufacturers can improve their production to increase speed and create less waste \cite{LF09}.

Learning becomes easy by using the principle of Occam's razor: We simply find the smallest program consistent with the data \cite{LF09}. Near perfect vision recognition, language comprehension and translation and all other learning tasks become trivial \cite{LF09}. We will also have much better predictions of weather and earthquakes and other natural phenomenon \cite{LF09}.

There would be disruption, including maybe displacing programmers \cite{IMP95}. The practice of programming itself would be more about gathering training data and less about writing code \cite{IMP95}. Google would have the resources to excel in such a world \cite{IMP95}.

But such changes may pale in significance compared to the revolution an efficient method for solving $\textit{NP--complete}$ problems will cause in mathematics itself. Research mathematicians spend their careers trying to prove theorems, and some proofs have taken decades or even centuries to find after problems have been stated. For instance, Fermat's Last Theorem took over three centuries to prove. A method that is guaranteed to find proofs to theorems, should one exist of a $``$reasonable$"$ size, would essentially end this struggle \cite{CS00}.

>>>>

In previous years there has been great interest in the verification or checking of computations \cite{LIP90}. Interactive proofs introduced by Goldwasser, Micali and Rackoff and Babi can be viewed as a model of the verification process \cite{LIP90}. Dwork and Stockmeyer and Condon have studied interactive proofs where the verifier is a space bounded computation instead of the original model where the verifier is a time bounded computation \cite{LIP90}. In addition, Blum and Kannan has studied another model where the goal is to check a computation based solely on the final answer \cite{LIP90}. More about probabilistic logarithmic space verifiers and the complexity class $NP$ has been investigated on a technique of Lipton \cite{LIP90}. In this work, we show some results about the logarithmic space verifiers applied to the class $NP$ and logarithmic space disqualifiers applied to the class $coNP$ which solve one of the most important open problems in computer science, that is $P$ versus $NP$.

@@

A logarithmic space transducer is a Turing machine with a read-only input tape, a write-only output tape, and read/write work tapes \cite{MS06}. The work tapes must contain at most $O(\log n)$ symbols \cite{MS06}. A logarithmic space transducer $M$ computes a function $f : \Sigma^{*} \rightarrow \Sigma^{*}$, where $f(w)$ is the string remaining on the output tape after $M$ halts when it is started with $w$ on its input tape \cite{MS06}. We call $f$ a logarithmic space computable function \cite{MS06}. We say that a language $L_{1} \subseteq \{0, 1\}^{*}$ is logarithmic space reducible to a language $L_{2} \subseteq \{0, 1\}^{*}$, written $L_{1} \leq_{l} L_{2}$, if there exists a logarithmic space computable function $f : \{0, 1\}^{*} \rightarrow \{0, 1\}^{*}$ such that for all $x \in \{0, 1\}^{*}$,
\[x \in L_{1} \textit{ if and only if } f(x) \in L_{2}.\]
The logarithmic space reduction is used in the definition of the complete languages for the classes $L$ and $NL$ \cite{Pap03}. A Boolean formula is in 2-conjunctive normal form, or $2CNF$, if it is in $CNF$ and each clause has exactly two distinct literals. There is a problem called $2SAT$, where we asked whether a given Boolean formula $\phi$ in $2CNF$ is satisfiable. $2SAT$ is complete for $NL$ \cite{Pap03}. Another special case is the class of problems where each clause contains $XOR$ (i.e. exclusive or) rather than (plain) $OR$ operators. This is in $P$, since an $\textit{XOR SAT}$ formula can also be viewed as a system of linear equations mod $2$, and can be solved in cubic time by Gaussian elimination \cite{MM11}. We denote the $XOR$ function as $\oplus$. The $\textit{XOR 2SAT}$ problem will be equivalent to $\textit{XOR SAT}$, but the clauses in the formula have exactly two distinct literals. $\textit{XOR 2SAT}$ is in $L$ \cite{AR00}, \cite{RM08}.

@@

\begin{hypothesis}
\label{hypothesis1}
Given a nonempty language $L_{1} \in L$, there is a language $L_{2}$ in $\textit{NP--complete}$ with a deterministic Turing machine $M$, where:
\[L_{2} = \{w: M(w, u) = y, \exists \textit{ string } u \textit{ such that } y \in L_{1}\}\]
when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$. In this way, there is an $\textit{NP--complete}$ language defined by a logarithmic space verifier $M$ such that when the input is an element of the language with its certificate, then $M$ outputs a string which belongs to a single language in $L$.
\end{hypothesis}

@@

$coNL$ is the complexity class containing the languages such that their complements belong to $NL$ \cite{Pap03}. We can give a disqualification-based definition for $coNL$ \cite{AB09}. The disqualification-based definition of $coNL$ assumes that a logarithmic space Turing machine has another separated read-only tape, that is the same kind of special tape called $``$read-once$"$ that we use in the certificate-based definition for $NL$ \cite{AB09}. Besides, in the disqualification-based definition of $coNL$, we assume the disqualification string is appropriated for the instance \cite{Pap03}. For example, a truth assignment for a Boolean formula $\phi$ in $3CNF$ is appropriated for the instance when every possible variable in $\phi$ could be evaluated in that truth assignment string, but we cannot affirm the same for every possible binary string.

@@

\begin{hypothesis}
\label{hypothesis2}
Given a nonempty language $L_{1} \in 1NL$, there is a language $L_{2}$ in $\textit{coNP--complete}$ with a deterministic Turing machine $M$, where:
\[L_{2} = \{w: M(w, u) = y, \forall \textit{ appropriated string } u \textit{ such that } y \in L_{1}\}\]
when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$. In this way, there is a $\textit{coNP--complete}$ language defined by a logarithmic space disqualifier $M$ such that when the input is an element of the language with any of its appropriated disqualification, then $M$ always outputs a string which belongs to a single language in $1NL$.
\end{hypothesis}

@@

\begin{theorem}
\label{proof}
There is a deterministic Turing machine $M$, where:
\[MAX\oplus2SAT = \{w: M(w, u) = y, \exists \textit{ string } u \textit{ such that } y \in \textit{XOR 2SAT}\}\]
when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
\end{theorem}

@@

\begin{proof}
Given a collection of integers $C$, we can read its elements from left to right, verify that every element is not equal to $0$, check that every element in $C$ has the same bit-length and count the amount of elements in $C$ to finally multiply it by $3$ and compare its bit-length with the single bit-length from the elements in $C$. In addition, we can nondeterministically pick two elements $a$ and $b$ from $C$ and accept in case of $a + b = 0$ otherwise we reject. We can make all this computation in a nondeterministic one-way using logarithmic space. Certainly, the calculation and store of the bit-length of the elements in $C$ could be done in logarithmic space since this is a unique value. On the one hand, we can count and store the number of elements that we read from the input and multiply it by $3$ to finally compare its bit-length with the stored bit-length, since the cardinality of $C$ multiplied by $3$ could be stored in a binary number of bit-length that is logarithmic in relation to the encoded length of $C$. On the other hand, the two elements $a$ and $b$ that we pick from $C$ have a logarithmic space in relation to the encoded length of $C$, because of every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$. Indeed, we never need to read to the left on the input for the acceptance of the elements in $\textit{SUM--ZERO}$ in a nondeterministic logarithmic space.
\end{proof}

\begin{theorem}
\label{demonstration}
There is a deterministic Turing machine $M$, where:
\[3UNSAT = \{w: M(w, u) = y, \forall \textit{ appropriated string } u \textit{ such that } y \in \textit{SUM--ZERO}\}\]
when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
\end{theorem}

@@

\begin{algorithm}
\caption{Logarithmic space disqualifier}\label{algorithm2}
\begin{algorithmic}[1]
\Comment{A valid instance for $3UNSAT$ with its disqualification}
\Procedure{$\textit{DISQUALIFIER}$}{$\phi, A$}
\Comment{Initialize an index}
\State $j \gets 0$
\Comment{$m$ is the number of clauses in $\phi$}
\Comment{Iterate for the elements of the disqualification array $A$}
\For{$i$}{$1$}{$m + 1$}
\If{$i = m+1$}
\Comment{There exists an $m+1$ element in the array}
\If{$A[i] \neq \textit{undefined}$}
\Comment{Reject the disqualification}
\State \textbf{return} $``no"$
\EndIf
\Comment{Break the $\textbf{for}$ loop}
\State \textbf{break}
\ElsIf{$A[i] = \textit{undefined} \vee A[i] < 1 \vee A[i] > 3$}
\Comment{Reject the disqualification}
\State \textbf{return} $``no"$
\Else
\State $j \gets A[i]$
\EndIf
\Comment{From the indexed $i^{th}$ clause $c_{i} = (x_{j} \vee y_{k} \vee z_{r})$ in $\phi$}
\Comment{Where $x$, $y$ and $z$ are literals with local indexes $\{j, k, r\} = \{1,2,3\}$ in $c_{i}$}
\Comment{Output the integer representation of the $j^{th}$ literal}
\Comment{Filled with zeroes to the left until a total of $|3 \times m|$ bits including the literal}
\Comment{But, the bit-length of the symbol minus is ignored in filling the negated literals}
\State \textbf{output} $``,x_{j}"$
\EndFor
\EndProcedure
\end{algorithmic}
\end{algorithm}
\end{proof}

@@

\begin{proof}
Since we have either $L \neq NL$ or $L = NL$ is true, then the complexity class $P$ is equal to $NP$.
\end{proof}

@@

No one has been able to find a polynomial time algorithm for any of more than $300$ important known $\textit{NP--complete}$ problems \cite{GJ79}. A proof of $P = NP$ will have stunning practical consequences, because it leads to efficient methods for solving some of the important problems in $NP$ \cite{CS00}. The consequences, both positive and negative, arise since various $\textit{NP--complete}$ problems are fundamental in many fields \cite{CS00}. The following consequences are assuming that we have a practical solution for the $\textit{NP--complete}$ problems where such existence was proven with our nonconstructive result:

\begin{enumerate}
\item Cryptography, for example, relies on certain problems being difficult. A constructive and efficient solution to an $\textit{NP--complete}$ problem such as $3SAT$ will break most existing cryptosystems including: Public-key cryptography \cite{HW97}, symmetric ciphers \cite{MM00} and one-way functions used in cryptographic hashing \cite{DKV07}. These would need to be modified or replaced by information-theoretically secure solutions not inherently based on $\textit{P--NP}$ equivalence.
\item There are enormous positive consequences that will follow from rendering tractable many currently mathematically intractable problems. For instance, many problems in operations research are $\textit{NP--complete}$, such as some types of integer programming and the traveling salesman problem \cite{GJ79}. Efficient solutions to these problems have enormous implications for logistics \cite{CS00}. Many other important problems, such as some problems in protein structure prediction, are also $\textit{NP--complete}$, so this will spur considerable advances in biology \cite{BL98}.
\item Since all the $\textit{NP--complete}$ optimization problems become easy, everything will be much more efficient \cite{LF09}. Transportation of all forms will be scheduled optimally to move people and goods around quicker and cheaper \cite{LF09}. Manufacturers can improve their production to increase speed and create less waste \cite{LF09}. Learning becomes easy by using the principle of Occam's razor: We simply find the smallest program consistent with the data \cite{LF09}. Near perfect vision recognition, language comprehension and translation and all other learning tasks become trivial \cite{LF09}. We will also have much better predictions of weather and earthquakes and other natural phenomenon \cite{LF09}.
\item There would be disruption, including maybe displacing programmers \cite{IMP95}. The practice of programming itself would be more about gathering training data and less about writing code \cite{IMP95}. Google would have the resources to excel in such a world \cite{IMP95}.
\item But such changes may pale in significance compared to the revolution an efficient method for solving $\textit{NP--complete}$ problems will cause in mathematics itself \cite{CS00}. Research mathematicians spend their careers trying to prove theorems, and some proofs have taken decades or even centuries to find after problems have been stated \cite{AS17}. For instance, Fermat's Last Theorem took over three centuries to prove \cite{AS17}. A method that is guaranteed to find proofs to theorems, should one exist of a $``$reasonable$"$ size, would essentially end this struggle \cite{CS00}.
\end{enumerate}
